Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-03 cikm2016/mdl.tex
API readability.

\subsection{Domains}
Potter's Wheel presents an algorithm for deriving a common structure for a set of strings by breaking each string down into a sequence of \textit{domains}. A domain is a set of strings, with a few optional statistical properties. They are defined by an interface that includes:
\begin{itemize}
\setlength\itemsep{0em}
\item A required inclusion function to test for membership in the domain (\functionname{match}). 
(\eg the domain \functionname{<Digits>} returns true for \functionname{"123"} 
and false for \functionname{"abc"}.)
\item An optional function to compute the number of values in the domain with a given length (\functionname{cardinality}).
(\eg the domain for three letter month names (\functionname{MMM}) would return $12$ for the length $3$ and $0$ otherwise.)
\item An optional function to update statistics for the domain based on a given value (\functionname{updateStatistics}).
(\eg the domain \functionname{MMM} might keep a histogram of how frequently each month was encountered.)
\item An optional function to prevent consideration of a domain that is redundant (\functionname{isRedundantAfter}).
(\eg  the domain \functionname{<Digits>} would be redundant after itself because there is no difference between a single run of digits and two adjacent runs.)
\end{itemize}

>>>>

\subsection{Domains}
Potter's Wheel presents an algorithm for deriving a common structure for a set of strings by breaking each string down into a sequence of \textit{domains}. A domain is a set of strings, with a few optional statistical properties. They are defined by an interface that includes:
\begin{itemize}
\setlength\itemsep{0em}
\item A required inclusion function \functionname{match} to test for membership in the domain
(\eg the domain \functionname{<Digits>} returns true for \functionname{"123"} 
and false for \functionname{"abc"}.)
\item An optional function \functionname{cardinality} to compute the number of values in the domain with a given length
(\eg the domain for three letter month names (\functionname{MMM}) would return $12$ for the length $3$ and $0$ otherwise.)
\item An optional function \functionname{updateStatistics} to update statistics for the domain based on a given value
(\eg the domain \functionname{MMM} might keep a histogram of how frequently each month was encountered.)
\item An optional function \functionname{isRedundantAfter} to prevent consideration of a domain that is redundant.
(\eg  the domain \functionname{<Digits>} would be redundant after itself because there is no difference between a single run of digits and two adjacent runs.)
\end{itemize}
